Data Specialization for a Staged Lambda Calculus

### 2014-11-05 paper/splitting.tex
One quick elaboration in section 4.

Splitting a stage \bbtwo\ term $\coltwo e A$ produces a \emph{precomputation}
term $p$ and a \emph{resumer} function $l.r$, which contain all stage \bbone\
and \bbtwo\ subcomputations of $e$, respectively. Since stage \bbtwo\
computations can depend on stage \bbone\ computations, $r$ can depend on $p$ via
the variable $l$. The correctness of splitting thus requires that evaluating
$\letin l p r$ agrees with the value to which $e$ itself evaluates.

\ur{I would not say that ``The correctness of splitting requires'',
  because we don't know what splitting is.  Instead, it is better to
  state this actively, e.g., say that we wish to split the code such
  that the condition e = let l = p in r holds.  correctness will have
  to go beyond this, by saying for example that all stage 1 parts are
  in p etc.  Note that this correctness allows a trivial split
   that shoves everything to r, e.g., p = () and r is ``e''
  (might need to flatten).}

>>>>

Splitting a stage \bbtwo\ term $\coltwo e A$ produces a \emph{precomputation}
term $p$ and a \emph{resumer} function $l.r$, which contain all stage \bbone\
and \bbtwo\ subcomputations of $e$, respectively. Since stage \bbtwo\
computations can depend on its stage \bbone\ computations within $e$, 
$r$ must depend on $p$, which splitting accomplishes via the variable $l$. 
Given this form, the goal for splitting is to ensure that evaluating
$\letin l p r$ agrees with the value to which $e$ itself evaluates.

\ur{Correctness will have
  to go beyond this, by saying for example that all stage 1 parts are
  in p etc.  Note that this correctness allows a trivial split
   that shoves everything to r, e.g., p = () and r is ``e''
  (might need to flatten).}
